The dictionary for characters of smooth group schemes

### 2016-05-23 followup.tex
Minor change - shift.
Added keywords, hyphenated one-dimensional to be consistent with the Abstract.

\subjclass[2010]{14F05 (primary), 14L15, 22E50}
\keywords{character sheaves}

@@

In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
Let $\gcs{L}$ be the geometric part of an object in $\CCS(G)$; see Section~\ref{sec:defs}.
Let $T$ be a maximal torus in $\bG$ and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
Then $\gcs{L}$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$.
It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields:
they are precisely those needed to describe one dimensional characters of such groups.
\bigskip

@@

We are extremely grateful to Loren Spice for explaining Yu's theory of types to us.
We also thank Masoud Kamgarpour for helpful conversations.

>>>>

\subjclass[2010]{14F05 (primary), 14L15, 22E50}
\keywords{function-sheaf dictionary, commutative character sheaves, types for supercuspidal representations}

@@

In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
Let $\gcs{L}$ be the geometric part of an object in $\CCS(G)$; see Section~\ref{sec:defs}.
Let $T$ be a maximal torus in $\bG$ and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
Then the perverse sheaf $\gcs{L}[\dim G]$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$ produced by parabolic induction.
It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields:
they are precisely those needed to describe one-dimensional characters of such groups.
\bigskip

@@

We are extremely grateful to Loren Spice for explaining Yu's types for supercuspidal representations.
We also thank Masoud Kamgarpour for helpful conversations.
